No Title

### 2017-10-27 paper/paper.tex
abstract

\begin{abstract}
We quantify the joint spatial distribution of the brightest satellites
around the Milky way and M31. 
We use the Illustris-1 and ELVIS simulations to show that the
MW satellite distribution is significantly thinner and more oblate
than the expectations from the Lambda Cold Dark Matter (LCDM)
paradigm. In contrast, the satellites in M31 are fully consistent with the
average expectations from simulations.
We also find that the satellite planes in the MW and M31 are almost perpendicular to the line
connecting the two galaxies. While none of the pairs in the simulations show
a similar degree of alignment, these alignments are consistent with a
random uniform distribution, making the result from the observations
consistent with these theoretical expectations.
The special satellite distribution in the Milky Way makes the Local
Group an atypical pair in the cosmological context provided by
LCDM simulations. 
We estimate that only $0.5\%$ to $1\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality, making
the LG a $3\sigma$ outlier in a sample of simulated galaxy pairs.
\end{abstract}

@@

\section{Data from the ELVIS simulation}
\label{sim:ELVIS}

\section{Data from the Illustris Simulation}
\label{sec:illustris}

@@

\begin{equation*}
\begin{bmatrix}
1.6  & 1.2 & 7.3\times10^{-1} & 7.9\times 10^{-2} & 1.0\times 10^{-1}
& 6.5\times 10^{-2}\\
 1.2  & 1.2 & 3.5\times10^{-1} & 8.9\times 10^{-3} & 1.5\times 10^{-2} &-7.4\times10^{-2}\\
 7.3\times10^{-1} & 3.5\times10^{-1} & 0.668 & 0.102 &-0.00331 & 0.151\\
 7.9\times 10^{-2}  & 8.9\times 10^{-3} & 0.102 & 0.474   & 0.695 &-0.127\\
 1.0\times 10^{-1}  & 1.5\times 10^{-2} &-0.003  &0.695  &1.48 &-0.695\\
 6.5\times 10^{-2} & -7.4\times10^{-2} & 0.151 &-0.127 &-0.695 & 0.607
\end{bmatrix}
\end{equation*}

@@

%MW mass
%https://arxiv.org/abs/1407.1078

>>>>

\begin{abstract}
We quantify the joint spatial distribution of the brightest satellites
around the Milky Way (MW) and M31, the dominant galaxies in the Local
Group (LG).
We use the Illustris-1 and ELVIS simulations to show that the
MW satellite distribution is significantly thinner and more oblate
than the expectations from the Lambda Cold Dark Matter (LCDM)
paradigm. In contrast, the satellites in M31 are fully consistent with the
average expectations from simulations.
We also find that the satellite planes in the MW and M31 are almost perpendicular to the line
connecting the two galaxies. While none of the pairs in the simulations show
a similar degree of alignment, these alignments are consistent with a
random uniform distribution, making the observations
consistent with theoretical expectations.
The special satellite distribution in the Milky Way makes the Local
Group an atypical pair in the cosmological context provided by
LCDM simulations. 
We estimate that only $0.5\%$ to $1\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality, making
the LG a $3\sigma$ outlier in a sample of simulated galaxy pairs.
\end{abstract}

@@

\section{Data from the ELVIS project}
\label{sim:ELVIS}

\section{Data from the Illustris project}
\label{sec:illustris}

@@

@@

%MW mass
%https://arxiv.org/abs/1407.1078
\appendix
